---
title: "WindsAndTemps"
author: "Charlie"
date: "3/25/2020"
output: pdf_document
---

But RMD is not the most convenient place to develop and debug code, so here we will read in all the code from another script file

```{r echo=FALSE,code = readLines("scripts/01-WindsAndTemps.R"), warning=FALSE, message=FALSE, results="hide", fig.show='hide' } 
# execute the script but suppresses all output
# basically this puts the script in memory (i.e., the Environment) so it can be used later
```

<!--```{r echo=FALSE,warning=FALSE, message=FALSE, results="hide", fig.show='hide',code = readLines("https://raw.githubusercontent.com/QFCatMSU/RMarkdown-Workshop-Material/master/scripts/01-WindsAndTemps.R"),  }
# Use if above does not work...
```-->

A Histogram of the change in temperature for the 366 days.  
```{r echo=FALSE}
  plot(plot1);
```

Boxplot for change in temperature by the prevailing wind direction.

```{r echo=FALSE}
  plot(plot2);
```

Boxplots faceting by the strength and direction of the wind

```{r echo=FALSE}
  plot(plot3);
```

If you want the code in the output file then you need to copy the code into the r block and set echo=TRUE

```{r echo=TRUE}
  #### Plot the histogram of the change in temperature
  plot1 = hist(changeTemp,
               main = "Daily change of average temperatures",
               xlab = "Change in Temperature (Fahrenheit)");
```