---
title: "WindsAndTemps"
author: "Charlie"
date: "3/25/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r echo=FALSE,code = readLines("scripts/01-WindsAndTemps.R"), warning=FALSE, message=FALSE, results="hide", fig.show='hide' } 
```

<!--```{r echo=FALSE,warning=FALSE, message=FALSE, results="hide", fig.show='hide',code = readLines("https://raw.githubusercontent.com/QFCatMSU/RMarkdown-Workshop-Material/master/scripts/01-WindsAndTemps.R"),  }
```-->

## Now, we really get into Rmarkdown! 

### Headers
For simplicity (and accessibility) in RMarkdown, it is best to use the header structure.  You can create headers in your document by using the number sign (\#).  The number of number signs give the header number -- you can use H1 (\#) through H6 (\######).  

### Bold and italics

**Bold** uses two asterisks and *italics* use one asterisk (\*).   And, yes, we can combine ***bold and italics*** using three asterisks!

### Escape characters
What happens when you want print out an command character instead of running the command?  You have already seen me use these above. We used an **escape character**, which in Rmarkdown is a backslash (\\).  And you can even escape a backslash with another backslash \\\\\\ -- 6 consecutive backslashes prints out 3 backslashes.

### Lists
1) Well RMD tries to manage your lists
    a) it is not robust
    b) and not always pretty
2) But in a pinch
    * it tends to work
    * You just have to remember to indent each level by 4 spaces
         * A third level... 8 spaces over
    * Notice that unordered lists use the same symbol as italics but without an end asterisk -- that can be awkward!

### Tables
| RMD   | is Good | For Quick | And Dirty  | Tables |
|------:|:--------|:---------:|------------|--------|
|But it | is      | limited   |in        |functionality|
| So    |   keep  |           | it         | simple! |
|Pipes | set | the | columns | and|
|dashes | and colons | set the | header and | alignment |

### Subscript and superscripts
Subscript uses tildes (\~) and superscripts use carrots (\^)  
E = m~r~c^2^: Energy of rest mass  

But, if you want to do formula more complicated than that, then you need LaTeX (or MathML)

## Advanced topics

### Greek Letters (using LaTeX)
alpha: $\alpha$  
beta: $\beta$  
gamma: $\gamma$  

### Add color to your text  
This <span style="color:blue;"> is blue only </span> in HTML  
This \textcolor{red}{is red only} in PDF

```{r echo=FALSE, fig.height=3, fig.width=4, fig.align="left"}
plot(plot1);
```

Boxplot for change in temperature by the prevailing wind direction

```{r echo=FALSE, fig.height=4.5, fig.width=5, fig.align="right"}
plot(plot2);
```

Boxplots faceting by the strength and direction of the wind

```{r echo=FALSE, fig.height=3, fig.width=4.5, fig.align="center"}
plot(plot3);
```

