---
title: "WindsAndTemps"
author: "Charlie"
date: "3/25/2020"
output: pdf_document
---

<!--
```{r echo=FALSE,code = readLines("scripts/01-WindsAndTemps.R"), warning=FALSE, message=FALSE, results="hide", fig.show='hide' } 
# execute the script but suppress all output
# basically this puts the script in memory so it can used later
```
-->

```{r echo=FALSE,warning=FALSE, message=FALSE, results="hide", fig.show='hide',code = readLines("https://raw.githubusercontent.com/QFCatMSU/RMarkdown-Workshop-Material/master/scripts/01-WindsAndTemps.R"),  }
# execute the script but suppress all output
# basically this puts the script in memory so it can used later
```

## Now, we really get into Rmarkdown! 

### Headers
For simplicity (and accessibility) in RMD, it is best to use the header structure.  You can create headers in your document by using the number sign (\#).  The number of number signs give the header number -- you can use H1 (\#) through H6 (\######).  

### Bold and italics

**Bold** uses two asteris and *italics* use one asterisjx (\*).   And, yes, we can combine ***bold and italics*** using three asterisks!

### Escape characters
 What happens when you want to actualy print out an command character instead of running the command?  You have already seen me use these above. WE used what are called **escape character**, which, in Rmarkdown, is a backslash.  And you can even escape a backslash with another backslash \\\\\\.  See!  6 consecutive backslashes prints out 3 backslashes.

### Lists
1) Well RMD tries to manage your lists
    a) it is not robust
    b) and not always pretty
2) But in a pinch
    * it tends to work
    * You just have to remember to indent each level by 4 spaces
         * A third level... 8 spaces over
    * Notice that unordered lists use the same symbol as italics but without an end asterisk -- that can be awkward!

### Tables
| RMD   | is Good | For Quick | And Dirty  | Tables |
|------:|:--------|:---------:|------------|--------|
|But it | is      | limited   |in        |functionality|
| So| keep || it | simple! |
|Pipes | set | the | columns | and|
|dashes | and colons | set the | header and | alignment |

### Subscript and superscripts
Subscript uses tildes (\~) and superscripts use carrots (\^)  
E = m~r~c^2^: Energy of rest mass  

But, if you want to do formula more complicated than that, then you need LaTeX (or MathML)

```{r echo=FALSE, fig.height=3, fig.width=4, fig.align="left"}
plot(plot1);
```

Boxplot for change in temperature by the prevailing wind direction

```{r echo=FALSE, fig.height=4.5, fig.width=5, fig.align="right"}
plot(plot2);
```

Boxplots facetting by the strength and direction of the wind

```{r echo=FALSE, fig.height=3, fig.width=4.5, fig.align="center"}
plot(plot3);
```
