---
title: "WindsAndTemps"
author: "Charlie"
date: "3/25/2020"
output: pdf_document
---

```{r echo=FALSE,code = readLines("scripts/01-WindsAndTemps.R"), warning=FALSE, message=FALSE, results="hide", fig.show='hide' } 
```

<!--```{r echo=FALSE,warning=FALSE, message=FALSE, results="hide", fig.show='hide',code = readLines("https://raw.githubusercontent.com/QFCatMSU/RMarkdown-Workshop-Material/master/scripts/01-WindsAndTemps.R"),  }
```-->

## Adding inline code and output to your document

### Inline Code
If you want to execute R code and output values to the document, then you use one apostrophe with an "r". For instance you can output the high temperature on the 100th day of the year: `r weatherData$maxTemp[100];` or the first ten values of the average temperature vector `r avgTemp[1:10];`.

You can put in more complex commands.  The mean of the change in temperature is: `r mean(changeTemp, na.rm=TRUE);`.  The highest change in temperature was `r max(changeTemp, na.rm=TRUE);`.  Or even put in multiple command -- the high temperature occurred on the day `r maxDayNum = which.max(changeTemp); maxDayNum;`, which is `r maxDay = weatherData$date[maxDayNum]; maxDay;`.  Or, written out is long format, that day is `r maxDay2 = as.Date(maxDay, format="%m-%d"); format(maxDay2, format="%B %d");`

## Code text format  
If you do not precede the code with an "r", then RMD will display it as code text: `this will be displayed as code text`, which means it will be displayed, rather than executed, in a monospaced format (all characters have the same width)


```{r echo=FALSE, fig.height=3, fig.width=4, fig.align="left"}
plot(plot1);
```

Boxplot for change in temperature by the prevailing wind direction

```{r echo=FALSE, fig.height=4.5, fig.width=5, fig.align="right"}
plot(plot2);
```

Boxplots faceting by the strength and direction of the wind

```{r echo=FALSE, fig.height=3, fig.width=4.5, fig.align="center"}
plot(plot3);
```
