---
title: "WindsAndTemps"
author: "Charlie"
date: "3/25/2020"
output: pdf_document
---

```{r echo=FALSE, code = readLines("scripts/01-WindsAndTemps.R"), warning=FALSE, message=FALSE, results="hide", fig.show='hide' }
# execute the script but suppress all output
# basically this puts the script in memory so it can used later
```

## Adding inline code and output to your document

### Inline Code
If you want to execute and display the value of R code, then you use one apostrophe. For instance you can output the high temperature on the 100th day of the year: `r weatherData$maxTemp[100];` or the first ten values of the average temperatures `r avgTemp[1:10];`.

You can put in more complex command like the mean of the change in temperature is: `r mean(changeTemp, na.rm=TRUE);`.  The highest change in temperature was `r max(changeTemp, na.rm=TRUE);`.  Or even put in mutiple command -- the high temperature occurred on the day `r maxDayNum = which.max(changeTemp); maxDayNum;`, which is `r maxDay = weatherData$date[maxDayNum]; maxDay;`.  Or, written out, that day is `r maxDay2 = as.Date(maxDay, format="%m-%d"); format(maxDay2, format="%B %d");`

IF you do not procede the code with an r, then RMD will display it as code text: `this will be displayed as code text`, which means it will be displayed, rather than executed, in a monospaced format (all characters have the same width)



```{r echo=FALSE, fig.height=3, fig.width=4, fig.align="left"}
plot(plot1);
```

Boxplot for change in temperature by the prevailing wind direction

```{r echo=FALSE, fig.height=4.5, fig.width=5, fig.align="right"}
plot(plot2);
```

Boxplots facetting by the strength and direction of the wind

```{r echo=FALSE, fig.height=3, fig.width=4.5, fig.align="center"}
plot(plot3);
```
