---
title: "WindsAndTemps"
author: "Charlie"
date: "3/25/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

<!-- Since I moved this Rmd file down one directory (to the docs folder), 
     I need to redo my file links and set the root directory in Rmd -->
     
<!-- This sets the root directory to the parent folder --
     The parent of docs is the root folder for this RStudio Project --> 
```{r setup}
knitr::opts_knit$set(root.dir = '../')
```

<!-- Changed scripts/01-WindsAndTemps.R to ../scripts/01-WindsAndTemps.R,
     which mean go back to folder folder and then go into the scripts folder -->
```{r echo=FALSE,code = readLines("../scripts/01-WindsAndTemps.R"), warning=FALSE, message=FALSE, results="hide", fig.show='hide' } 
```

### Task 3 Answers
Note: level 4 headers are inline headers in many documents

#### 3x4 Table with bolded and italicized values
| a     | perfectly   | boring  | table |
|-------|-------------|---------|-------|
|Hi, I am **bold**  | ***and I am bold and italics*** | X~2~ | x^2^ |
|Note that | pipe | positioning | does not matter |
|But the | number | of pipes | does|


#### Another list

1) My favorite animals
    a) Llamas
    b) Piping Plovers
    c) Guanacos
        * Yeah, guanacos and llamas are very similar, so that is kind of cheating
2) My favorite foods
    a) Schezwan
    b) Soup
    c) Middleeastern
3) My favorite Movies
    * I cannot think right now about this 
    * But, you get the point of lists
        * Right?
    
#### Print weird characters

\*\\\\\* \$\^\& 

#### Print formulas

V~cyl~ = $\pi$r^2^h  
Anything more complicated really required LaTeX or MathML


## Now, we really get into Rmarkdown! 

### Headers
For simplicity (and accessibility) in RMarkdown, it is best to use the header structure.  You can create headers in your document by using the number sign (\#).  The number of number signs give the header number -- you can use H1 (\#) through H6 (\######).  

### Bold and italics

**Bold** uses two asterisks and *italics* use one asterisk (\*).   And, yes, we can combine ***bold and italics*** using three asterisks!

### Escape characters
What happens when you want print out an command character instead of running the command?  You have already seen me use these above. We used an **escape character**, which in Rmarkdown is a backslash (\\).  And you can even escape a backslash with another backslash \\\\\\ -- 6 consecutive backslashes prints out 3 backslashes.

### Lists
1) Well RMD tries to manage your lists
    a) it is not robust
    b) and not always pretty
2) But in a pinch
    * it tends to work
    * You just have to remember to indent each level by 4 spaces
         * A third level... 8 spaces over
    * Notice that unordered lists use the same symbol as italics but without an end asterisk -- that can be awkward!

### Tables
| RMD   | is Good | For Quick | And Dirty  | Tables |
|------:|:--------|:---------:|------------|--------|
|But it | is      | limited   |in        |functionality|
| So| keep || it | simple! |
|Pipes | set | the | columns | and|
|dashes | and colons | set the | header and | alignment |

### Subscript and superscripts
Subscript uses tildes (\~) and superscripts use carrots (\^)  
E = m~r~c^2^: Energy of rest mass  

But, if you want to do formula more complicated than that, then you need LaTeX (or MathML)

## Advanced topics

### Greek Letters (using LaTeX)
alpha: $\alpha$  
beta: $\beta$  
gamma: $\gamma$  

### Add color to your text  
This <span style="color:blue;"> is blue only </span> in HTML  
This \textcolor{red}{is red only} in PDF

```{r echo=FALSE, fig.height=3, fig.width=4, fig.align="left"}
plot(plot1);
```

Boxplot for change in temperature by the prevailing wind direction

```{r echo=FALSE, fig.height=4.5, fig.width=5, fig.align="right"}
plot(plot2);
```

Boxplots faceting by the strength and direction of the wind

```{r echo=FALSE, fig.height=3, fig.width=4.5, fig.align="center"}
plot(plot3);
```

