---
title: "WindsAndTemps"
author: "Charlie"
date: "3/25/2020"
output: pdf_document
---

<!-- Since I moved this Rmd file down one directory (to the docs folder), 
     I need to redo my file links and set the root directory in Rmd -->
     
<!-- This sets the root directory to the parent folder --
     The parent of docs is the root folder for this RStudio Project --> 
```{r setup}
knitr::opts_knit$set(root.dir = '../')
```

<!-- Changed scripts/01-WindsAndTemps.R to ../scripts/01-WindsAndTemps.R,
     which mean go back to folder folder and then go into the scripts folder -->
```{r echo=FALSE,code = readLines("../scripts/01-WindsAndTemps.R"), warning=FALSE, message=FALSE, results="hide", fig.show='hide' } 
```

## Answers from Task 4

### Information about `avgTemp`

The highest average temperature for 2016 in Lansing was `r max(avgTemp);` on `r maxIndex = which.max(avgTemp); weatherData$date[maxIndex];`, the lowest average temperature was `r min(avgTemp);`  on `r minIndex = which.min(avgTemp); weatherData$date[minIndex];`, and the average of all average temperatures was `r mean(avgTemp);` with the median average temperature being `r median(avgTemp);`.

#### Same paragraph using Celsius temperatures:  
The highest average temperature for 2016 in Lansing was `r (5/9) * (max(avgTemp)-32);` on `r maxIndex = which.max(avgTemp); weatherData$date[maxIndex];`, the lowest average temperature was `r (5/9) * (min(avgTemp)-32);`  on `r minIndex = which.min(avgTemp); weatherData$date[minIndex];`, and the average of all average temperatures was `r (5/9) * (mean(avgTemp)-32);` with the median average temperature being `r (5/9) * (median(avgTemp)-32)`.

#### Same paragraph using Celsius temperatures and 3 significant digits:  
The highest average temperature for 2016 in Lansing was `r signif((5/9) * (max(avgTemp)-32), 3);` on `r maxIndex = which.max(avgTemp); weatherData$date[maxIndex];`, the lowest average temperature was `r signif((5/9) * (min(avgTemp)-32), 3);`  on `r minIndex = which.min(avgTemp); weatherData$date[minIndex];`, and the average of all average temperatures was `r signif((5/9) * (mean(avgTemp)-32), 3);` with the median average temperature being `r signif((5/9) * (median(avgTemp)-32), 3)`.

### Table of weather data: 
<!-- Set this up for easier access in the table -->
`r minIndex = which.min(avgTemp); rmaxIndex = which.max(avgTemp);`

|     |Temp | Date | Humidity | Wind Speed (average) | Prevailing Wind Direction |
|-|:-:|:-:|:-:|:-:|:-:|
|minimum | `r avgTemp[minIndex]` | `r weatherData$date[minIndex]` | `r weatherData$relHum[minIndex]` | `r weatherData$windSpeed[minIndex]` | `r weatherData$windDir[minIndex]` |
|maximum | `r avgTemp[maxIndex]` | `r weatherData$date[maxIndex]` | `r weatherData$relHum[maxIndex]` | `r weatherData$windSpeed[maxIndex]` | `r weatherData$windDir[maxIndex]` |


